---
title: "TinyTags"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
setwd("/home/claire/OneDriveDoc/Doc doc doc/Ph.D. - ANALYSES/R analysis/Data")

L <- read.csv("LAREN_inc_geese_V2.csv")
C <- read.csv("2017_TT_infos.csv")
```

## Data to merge
```{r}
summary(L)
```
* socle = ID of TinyTag
* ttag_exp_start = the starting point of the profil for computation
* ttag_exp_end = the ending point of the profil for computation
* nbrecess = number of recesses
* lengthrecess = total duration of recesses
* inc_prop = proportion of time dedicated to incubation
* meanrecess = mean duration of recesses (= lengthrecess / nbrecess)
* meanfreq = mean frequency of recesses per 24h (nbrecess / nb total de minute * 1400 (soit 24h))

```{r}
summary(C)
```
* socle = ID of TinyTag
* DEPLOY = date of deployment (JJ)
* MANIP_SONDE = 0 if there was no TinyTag manipulation, = 1 if there was at least one TinyTag manipulation
* RECUP_... = day (JJ) or hour of the TinyTag recuperation
* ISSUE = 0 for fail and 1 for success
* ISSUE_DATE = day where the nest issue was noted
* CLUTCH = minimal clutch size
* PREDPAR = 1 if there was at least one partial predation, = 0 if there was not

## Merged data
```{r}
full <- merge(L, C, "socle")
head(full)
```

## Obtaining the total duration of TinyTags recording used to compute variables
```{r, message = FALSE}
require(lubridate)
#Setting dates as dates
full$ttag_exp_start <- as.POSIXct(full$ttag_exp_start, tz = "America/Toronto", format = "%Y-%m-%d %H:%M:%S")
full$ttag_exp_end <- as.POSIXct(full$ttag_exp_end, tz = "America/Toronto", format = "%Y-%m-%d %H:%M:%S")
full$ttag_duration <- as.numeric((full$ttag_exp_end - full$ttag_exp_start)*24*60) # in minutes
full$lengthinc <- full$ttag_duration - full$lengthrecess

# To check ... MISMATCH
full$inc_propV2 <- full$lengthinc / full$ttag_duration
full[,c(1, 7, 26)]
```